---
title: "Fermented Food in Numbers"
output: 
  flexdashboard::flex_dashboard:

    css: style.css
    social: menu
    source_code: embed
    orientation: columns
    vertical_layout: fill
 
---
```{r setup, include=FALSE}
#------------------ Packages ------------------
library(flexdashboard)
library(dplyr)
library(DT)
library(plotly)
library(leaflet)
library(rnaturalearth)
library(ggplot2)
library(readxl)
library(tidyr)
#------------ Country cleanup ---------------------
country.table <- read.csv("country.csv")
fermentedfood.new <- read_excel("FermFood_new.xlsx", .name_repair = function(x) gsub("\\s+", "_", x))

fermentedfood.flat <- separate_longer_delim(fermentedfood.new,c(Country,Country_code),delim = ',')
fermentedfood.flat$Country_code <- as.integer(fermentedfood.flat$Country_code)

```

Map {data-orientation=rows}
===================================== 

Row {data-height=50}
----------------------------------
### Total number of fermented products
```{r}
valueBox(value = dplyr::n_distinct(fermentedfood.new$Product), 
         icon = "fas fa-carrot", 
         color = "info"
         )
```
### Category 
```{r}
valueBox(value =  dplyr::n_distinct(fermentedfood.new$Category), 
         icon = "fas fa-leaf", 
         color = 'success'
         )
```
### Ontology groups 
```{r}
valueBox(value = dplyr::n_distinct(fermentedfood.new$Raw_material_ontology),
         icon = "fas fa-seedling",
         color = 'success'
        )
```

### Country
```{r}
valueBox(value = dplyr::n_distinct(fermentedfood.flat$Country),
         icon = "fas fa-globe", 
        )
```

Row {data-height=800}
-----------------------------------------------------------------------

###  
```{r}

fermentedfood.country <- select(fermentedfood.flat,Country_code,Product) %>%
                              left_join(select(country.table,name,region,sub.region,country.code,alpha.3),
                             by = c('Country_code' = 'country.code'))

# map polygons coordinates
map <- ne_countries()
names(map)[names(map) == "iso_a3_eh"] <- "ISO3"
names(map)[names(map) == "name"] <- "NAME"

# all countries iso codes
country.table<-country.table %>% select(3:3)
fermentedfood.agg <- na.omit(fermentedfood.country %>% group_by(alpha.3) %>% 
  summarise(total_count=n(),
            .groups = 'drop'))

fermentedfood.joined <- left_join(country.table, fermentedfood.agg, by = 'alpha.3')

map$total_count <-fermentedfood.joined[match(map$ISO3, fermentedfood.joined$alpha.3),"total_count"]
# palete of colors
pal <- colorBin(palette = 'viridis', domain = map$total_count,
                bins = seq(0, max(map$total_count, na.rm = TRUE) +15, by = 2))


map$labels <- paste0("<strong> Country: </strong> ", map$NAME, "<br/> ",
                     "<strong> Total count: </strong> ", map$total_count, "<br/> ") %>%
                       lapply(htmltools::HTML)

leaflet(map) %>% 
  addTiles() %>% 
    setView(lng = 10, lat = 40, zoom = 3) %>%
    addPolygons(
    fillColor = ~pal(total_count),
    color = "white",
    fillOpacity = 0.7,
    label = ~labels,
    highlight = highlightOptions(color = "black", bringToFront = TRUE)) %>%
  addLegend(pal = pal, values = ~total_count, opacity = 0.7, title = "FermentedFood")

```

Graphs {data-orientation=columns}
===================================== 

Column {data-width=250} 
-------------------------------------- 

### bln liters of beer in 2022
```{r}
valueBox(value = 189, 
         icon="fa-solid fa-beer-mug-empty",
         color = "info"
         )
```

### bln liters of wine in 2022 

```{r}
valueBox(value =  25.8, 
         icon = "fa-solid fa-wine-glass", 
         color = 'success'
         )
```

### bln kg of bread in 2023
```{r}
valueBox(value = 185,
         icon ="fa-solid fa-bread-slice",
         color = 'success'
        )
```

###  bl kg of soy sauce in China (2021)

```{r}
valueBox(value = 7.9,
         icon = "fa-solid fa-bottle-water", 
        )
```
### bln kg of cheese in 2023

```{r}
valueBox(value = 22.35,
         icon = "fas fa-cheese", 
        )
```
###  bln kg og yogurt in 2023

```{r}
valueBox(value = 60.5,
         icon = "fa-solid fa-whiskey-glass", 
        )
```
Column {data-width=400}
--------------------------------------    

###

```{r}
fermentedfood.category <- fermentedfood.new %>% group_by(Category) %>% 
  summarise(total_count=n(),.groups = 'drop') %>%
  as.data.frame()
datatable(arrange(fermentedfood.category,desc(total_count)), rownames = FALSE,options = list(dom = 't')
          )
```
###

```{r}
fermentedfood.country <- fermentedfood.new %>% group_by(Country) %>% 
  summarise(total_count=n(),.groups = 'drop') %>%
  as.data.frame()
datatable(arrange(fermentedfood.country,desc(total_count)), rownames = FALSE,options = list(dom = 't')
          )
```



Column {data-width=400}
--------------------------------------    
```{r}

df_ontology <- read.csv('test_treemap.csv',header = TRUE)
fig <- plot_ly(
  type="treemap",
  labels=df_ontology$label,
  parents=df_ontology$parent
)
m <- list(
  l = 0,
  r = 0,
  b = 0,
  t = 0,
  pad = 4
)
fig <- fig %>% layout(autosize = F, width = 600, height = 700,margin = m)

fig

```
Data {data-orientation=rows}
===================================== 
```{r}
fermentedfood.new %>% 
  select(Continent,Region,Subregion,Country,Category,Product,Name_in_original_language,Description,Raw_material_ontology, Webpage_reference) %>%
  datatable(rownames = FALSE,
                colnames = c("Continent","Region",'Subregion',"Country","Category","Product","Name_in_original_language",
                "Description","Raw_material_ontology",  "Webpage_reference"
),
            options = list(searchHighlight = TRUE, 
                           pageLength = nrow(fermentedfood)), filter = 'top')
```

About {data-orientation=rows}
===================================== 
**The Fermented Food Dashboard**

Fermented food of the world integrated resource
“A comprehensive manually curated and referenced list of fermented foods of the world.”
The presented resource includes:






* Location:
Full country name(s), regions and subregions based on the classification provided by the Standard country or area codes for statistical use (M49) of the United Nations.
      
* Product (Name):
Name in English. If available, the name in the original language is also presented.
     
* Description:
Overview for a non-expert. (1) Overall description of the food (2) Particularities of the production; and (3) Particularities of location of production or geographic distribution.

* Raw material ontology:
This classification is based exclusively on raw materials on a semi-organismic level while excluding processing information.

* Raw material additional information:
Details about the raw materials that are not captured in the ontology. It includes any details related to the particularities of an ingredient.

* Category:
Each food is assigned to one general fermented food category:  acid beverage, alcoholic beverage, beer, cheese, condiment, dairy product, fermented cereal, fermented fish, fermented fruit, fermented legumes, fermented meat, fermented roots, fermented vegetables, or wine.

* References:
A valid reference from a peer-reviewed publication, book, industry handbook or official government document.

* Webpage reference:
Government website or Wikipedia webpages containing image of the fermented food.









**Code**

The code behind this dashboard is available on Github.


