---
title: "Fermented Food in Numbers"
output: 
  flexdashboard::flex_dashboard:

    css: style.css
    social: menu
    source_code: embed
    orientation: columns
    vertical_layout: fill
 
---
```{r setup, include=FALSE}
#------------------ Packages ------------------
library(flexdashboard)
library(dplyr)
library(DT)
library(plotly)
library(leaflet)
library(rnaturalearth)
library(ggplot2)
library(readxl)
library(tidyr)
#------------ Country cleanup ---------------------
country.table <- read.csv("country.csv")
fermentedfood.new <- read_excel("FermFood_new.xlsx", .name_repair = function(x) gsub("\\s+", "_", x))

fermentedfood.flat <- separate_longer_delim(fermentedfood.new,c(Country,Country_code),delim = ',')
fermentedfood.flat$Country_code <- as.integer(fermentedfood.flat$Country_code)

```

Map {data-orientation=rows}
===================================== 

Row {data-height=50}
----------------------------------
### Total number of fermented products
```{r}
valueBox(value = dplyr::n_distinct(fermentedfood.new$Product), 
         icon = "fas fa-carrot", 
         color = "info"
         )
```
### Category 
```{r}
valueBox(value =  dplyr::n_distinct(fermentedfood.new$Category), 
         icon = "fas fa-leaf", 
         color = 'success'
         )
```
### Ontology groups 
```{r}
valueBox(value = dplyr::n_distinct(fermentedfood.new$Raw_material_ontology),
         icon = "fas fa-seedling",
         color = 'success'
        )
```

### Country
```{r}
valueBox(value = dplyr::n_distinct(fermentedfood.flat$Country),
         icon = "fas fa-globe", 
        )
```

Row {data-height=800}
-----------------------------------------------------------------------

###  
```{r}

fermentedfood.country <- select(fermentedfood.flat,Country_code,Product) %>%
                              left_join(select(country.table,name,region,sub.region,country.code,alpha.3),
                             by = c('Country_code' = 'country.code'))

# map polygons coordinates
map <- ne_countries()
names(map)[names(map) == "iso_a3_eh"] <- "ISO3"
names(map)[names(map) == "name"] <- "NAME"

# all countries iso codes
country.table<-country.table %>% select(3:3)
fermentedfood.agg <- na.omit(fermentedfood.country %>% group_by(alpha.3) %>% 
  summarise(total_count=n(),
            .groups = 'drop'))

fermentedfood.joined <- left_join(country.table, fermentedfood.agg, by = 'alpha.3')

map$total_count <-fermentedfood.joined[match(map$ISO3, fermentedfood.joined$alpha.3),"total_count"]
# palete of colors
pal <- colorBin(palette = 'viridis', domain = map$total_count,
                bins = seq(0, max(map$total_count, na.rm = TRUE) +15, by = 2))


map$labels <- paste0("<strong> Country: </strong> ", map$NAME, "<br/> ",
                     "<strong> Total count: </strong> ", map$total_count, "<br/> ") %>%
                       lapply(htmltools::HTML)

leaflet(map) %>% 
  addTiles() %>% 
    setView(lng = 10, lat = 40, zoom = 3) %>%
    addPolygons(
    fillColor = ~pal(total_count),
    color = "white",
    fillOpacity = 0.7,
    label = ~labels,
    highlight = highlightOptions(color = "black", bringToFront = TRUE)) %>%
  addLegend(pal = pal, values = ~total_count, opacity = 0.7, title = "FermentedFood")

```

Graphs {data-orientation=columns}
===================================== 

Column {data-width=250} 
-------------------------------------- 

### bln liters of beer in 2022
```{r}
valueBox(value = 189, 
         icon="fa-solid fa-beer-mug-empty",
         color = "info"
         )
```

### bln liters of wine in 2022 

```{r}
valueBox(value =  25.8, 
         icon = "fa-solid fa-wine-glass", 
         color = 'success'
         )
```

### bln kg of bread in 2023
```{r}
valueBox(value = 185,
         icon ="fa-solid fa-bread-slice",
         color = 'success'
        )
```

###  bl kg of soy sauce in China (2021)

```{r}
valueBox(value = 7.9,
         icon = "fa-solid fa-bottle-water", 
        )
```
### bln kg of cheese in 2023

```{r}
valueBox(value = 22.35,
         icon = "fas fa-cheese", 
        )
```
###  bln kg og yogurt in 2023

```{r}
valueBox(value = 60.5,
         icon = "fa-solid fa-whiskey-glass", 
        )
```
Column {data-width=400}
--------------------------------------    

###

```{r}
fermentedfood.category <- fermentedfood.new %>% group_by(Category) %>% 
  summarise(total_count=n(),.groups = 'drop') %>%
  as.data.frame()
datatable(arrange(fermentedfood.category,desc(total_count)), rownames = FALSE,options = list(dom = 't')
          )
```
###

```{r}
fermentedfood.country <- fermentedfood.new %>% group_by(Country) %>% 
  summarise(total_count=n(),.groups = 'drop') %>%
  as.data.frame()
datatable(arrange(fermentedfood.country,desc(total_count)), rownames = FALSE,options = list(dom = 't')
          )
```



Column {data-width=400}
--------------------------------------    
```{r}

df_ontology <- read.csv('test_treemap.csv',header = TRUE)
fig <- plot_ly(
  type="treemap",
  labels=df_ontology$label,
  parents=df_ontology$parent
)
m <- list(
  l = 0,
  r = 0,
  b = 0,
  t = 0,
  pad = 4
)
fig <- fig %>% layout(autosize = F, width = 600, height = 700,margin = m)

fig

```
Data {data-orientation=rows}
===================================== 
```{r}
fermentedfood.new %>% 
  select(Continent,Region,Subregion,Country,Category,Product,Name_in_original_language,Description,Raw_material_ontology, Webpage_reference) %>%
  datatable(rownames = FALSE,
                colnames = c("Continent","Region",'Subregion',"Country","Category","Product","Name_in_original_language",
                "Description","Raw_material_ontology",  "Webpage_reference"
),
            options = list(searchHighlight = TRUE, 
                           pageLength = nrow(fermentedfood)), filter = 'top')
```

About {data-orientation=rows}
===================================== 
**The Fermented Food Dashboard**

Network visualization: In the table there are shared foods between the different countries.
It would be useful to show a graph where the nodes are countries 
(if possible also grouped by region, subregion, continent) and the edges are foods.
The size of the node could be determined by its weight and all edges would be unweighted.
If possible the user should be able to select the countries.


**Contributors** 

Rosanna Coda, Jan Patrick Tan



